\bf\mftitle

### 2011-01-21 doc/jInfer/twostep/twostep.tex
3159165 Create documentation fof TwoStep simplifier - state removal modules picture

Whole submodule structure of AutomatonMergingState cluster processor is drawn on fig. \ref{automaton_merging_state_submodules}.
\begin{figure}
	\centering\includegraphics[scale=\myscale]{automaton_merging_state_submodules}
	\caption{Submodules of AutomatonMergingState cluster processor} \label{automaton_merging_state_submodules}
\end{figure}
We have implemented \emph{k,h-context} (see \cite{ahonen}) state equivalence in class \code{KHContext}, which is used by \code{Greedy}
to test mergability of states by default configuration.

\subsubsection{StateRemoval}
We are using state removal method (see \cite{1224321}) to convert regexp automaton into equivalent regular expression.
This is implemented in \code{StateRemoval} class.
We defined one submodule of this class with interface called \code{Orderer}.
It has only one method to implement: \code{getStateToRemove}.
Given automaton it has to return reference to one state which should be removed from automaton at first.
State removal calls this submodule and removes states given until there are only two states in automaton - superInitial and superFinal states,
with exactly one transition.
That transition has final regular expression on it as symbol, it is read and returned to AutomatonMergingState.
We implement one orderer, called \code{Weighted}.
It is simple heuristic - weights all states (weight = sum of {in | out | loop}-transition regular expression lengths) and returns state with lowest weight.

>>>>

Whole submodule structure of AutomatonMergingState cluster processor is drawn on fig. \ref{automaton_merging_state_modules}.
\begin{figure}
	\centering\includegraphics[scale=\myscale]{automaton_merging_state_modules}
	\caption{Submodules of AutomatonMergingState cluster processor} \label{automaton_merging_state_modules}
\end{figure}
We have implemented \emph{k,h-context} (see \cite{ahonen}) state equivalence in class \code{KHContext}, which is used by \code{Greedy}
to test mergability of states by default configuration.

\subsubsection{StateRemoval}
\begin{figure}
	\centering\includegraphics[scale=\myscale]{state_removal_modules}
	\caption{Modules of StateRemoval.} \label{state_removal_modules}
\end{figure}
We are using state removal method (see \cite{1224321}) to convert regexp automaton into equivalent regular expression.
This is implemented in \code{StateRemoval} class (on fig. \ref{state_removal_modules}).
We defined one submodule of this class with interface called \code{Orderer}.
It has only one method to implement: \code{getStateToRemove}.
Given automaton it has to return reference to one state which should be removed from automaton at first.
State removal calls this submodule and removes states given until there are only two states in automaton - superInitial and superFinal states,
with exactly one transition.
That transition has final regular expression on it as symbol, it is read and returned to AutomatonMergingState.
We implement one orderer, called \code{Weighted}.
It is simple heuristic - weights all states (weight = sum of {in | out | loop}-transition regular expression lengths) and returns state with lowest weight.
